\documentclass{article}

\begin{document}

\begin{enumerate}

\item Do you consider yourself a visual learner?  (Yes) (No)

\item Using the visualization helped me learn and understand the algorithm (Agree) (Disagree)

\item The hypertextbook was helpful in understanding how and why the algorithm works
"                   " unclear or ambiguous in some sections

\item I read through some parts of the hypertext book more than once to improve my understanding of the topic (True) (False)

\item The guide was informative and helpful for setting up and using the visualization (for our own reference, not for research) %Do we tell them that?

\item Rank the following items with respect to how helpful you thought each was:
Use 1 for the most helpful, 5 for the least.
  The visualization pictures
  The pseudo-code tab
  The info tab
  The pop-up questions
  The color scheme (???)
  The exercises

\item
\begin{tabular}{| l | c | c | c | c |}
\hline
\textbf{Component} & \textbf{Used a lot} & \textbf{Used some} & \textbf{Hardly used} & \textbf{Did not use} \\
\hline
Visulization pictures &&&& \\
\hline
Visualization pseudo-code tab &&&& \\
\hline
Visualization info-tab &&&& \\
\hline
Visualization exercises &&&& \\
\hline
Provided textbook materials &&&& \\
\hline
Provided JHAVÉ guide &&&& \\
\hline
Other (please explain) &&&& \\
\hline
\end{tabular}

\item
\begin{tabular}{| l | c | c | c | c |}
\hline
\textbf{Component} & \textbf{Very helpful} & \textbf{Helpful} & \textbf{A little helfpul} & \textbf{Not helpful} \\
\hline
Visulization pictures &&&& \\
\hline
Visualization pseudo-code tab &&&& \\
\hline
Visualization info-tab &&&& \\
\hline
Visualization exercises &&&& \\
\hline
Provided textbook materials &&&& \\
\hline
Provided JHAVÉ guide &&&& \\
\hline
Other (please explain) &&&& \\
\hline
\end{tabular}

\item I sought other materials than those provided by my professor to learn this algorthim.
(True) (False)

If True, please indicate what materials were used.

\section*{Question Questions}

\item The use of colors in the visualization was confusing or unclear.
(Agree) (Disagree)

\item I frequently chose  the correct answer for the pop-up questions on my first attempt.
(Agree) (Disagree)
%What does this show?  Did you know we can record these statistics if we get Tom give them sign-in credentials?  Maybe too much work.  If its not already being done, we maybe should get JHAVÉ.org to start logging usage, user responses for data analysis ☺ unrelated to the task at hand though.

\item I frequently guessed on the pop-up questions.
(Agree) (Disagree)

\item The questions were ambiguous or confusing.
(Agree) (Disagree)

\section*{Other Questions}

\item The input generator was easy to understand and use.
(Agree) (Disagree)

\item Please indicate roughly how many different inputs you used with the visualization? \_\_\_\_

\item I could have learned the algorithm without the use of the visualization.
(Just a little more formal)


%These will be helpful for us but open ended questions will be hard to use in analysis unless many users say the same thing
\section*{Comments}

Regarding your overall experience using these materials to learn Booth's Multiplication Algorithm, please provide comments or improvement you would like to see, if any:

  Visualization:

  Textbook:

  Guide:

  Additional Thoughts or Comments:

\end{enumerate}

\end{document}
